### 2016-06-07 Chapters/paper1.tex
X

\section{Numerical experiments}\label{s-numex}
%
The purpose of this section is to show the results obtained with the methods proposed in this work when solving a set of common tests in the literature. In Algorithm \ref{alg-wNPS-GJV}  we collect the possible choices for the linear and nonlinear stabilization for the multidimensional transport problem. The wNPS linear stabilization has been combined with nGJV (monotonic scheme) and SUPG; we have also considered nGJV shock-capturing alone to justify the need of linear stabilization. Since bGJV does not enjoy any DMP, it is used together with SUPG stabilization in the numerical tests. Moreover the methods RV and EV are used together with SUPG linear stabilization and no extra stabilization respectively, because this is the way they are used in the literature.

>>>>

\section{Numerical experiments}\label{s-numex}
%
The purpose of this section is to show the results obtained with the previously proposed methods when solving a set of common tests in the literature. In Algorithm \ref{alg-wNPS-GJV}  we collect the possible choices for the linear and nonlinear stabilization for the multidimensional transport problem. The wNPS linear stabilization has been combined with nGJV (monotonic scheme) and SUPG; we have also considered nGJV shock-capturing alone to justify the need of linear stabilization. Since bGJV does not enjoy any DMP, it is used together with SUPG stabilization in the numerical tests. Moreover the methods RV and EV are used together with SUPG linear stabilization and no extra stabilization respectively, because this is the way they are used in the literature.
